Global adjoint tomography -- Model GLAD-M25

### 2019-01-28 main.tex
update window figures

Fig.~\ref{fig:window_density} shows a time-distance plot
for vertical component 17--40~s body waves in which the Pyflex window count is used to identify parts of seismograms being assimilated.
A total of 4,363,719 time windows were picked in this category.
The figure nicely highlights all the well known body traveltime branches.
The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins. Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }
  \label{fig:window_density}
\end{figure}

@@

@@

@@

In the 200--400~km depth range, we observe a high wavespeed
anomaly within the Gulf of Mexico, which coincides spatially with the deepest
bathymetry and corresponds to a portion of ancient oceanic
Lithosphere~\citep{muller2008}.
A remnant of the Juan de Fuca plate,
with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
where SL2013NA shows a much stronger anomaly.

>>>>

Fig.~\ref{fig:window_density_Z} shows a time-distance plot
for vertical component 17--40~s body waves in which the Pyflex window count is used to identify parts of seismograms being assimilated.
A total of 4,363,719 time windows were picked in this category.
The figure nicely highlights all the well known body traveltime branches.
The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins. Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }
  \label{fig:window_density_Z}
\end{figure}

Fig.~\ref{fig:window_density_R} and Fig.~\ref{fig:window_density_T} shows for Radial and Transverse component in 17--40~s period bands.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for Radial component 17--40~s body waves.}
  \label{fig:window_density_R}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for Transverse component 17--40~s body waves.}
  \label{fig:window_density_T}
\end{figure}

@@

Fig~\ref{fig:P_phase_hist} shows histograms of the phase measurements of first P
arrivals in two of the body wave measurement categories. All the
categories show consistent reduction in both mean and variance values. 
Although there are various phases assimilated and
P arrivals only contribute ~8\% of the overall measurements,
the histogram shows we are still doing a good job at minimizing the
misfit of the P arrivals.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
  \caption{Histograms of phase measurements of P arrivals in two measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}). Other settings are the same as Fig.~\ref{fig:phase_hist}. }
  \label{fig:P_phase_hist}
\end{figure}

@@

P phase measurements were also extracted and compared in Fig.~\ref{fig:phase_hist_360_P} for 3 models. The behavior is consistent as we expected.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_360_P.pdf}
  \caption{Histograms of phase measurements of P arrivals for the 360 events in the held-out database in Vertical and Radial 17--40~s period band .}
  \label{fig:phase_hist_360_P}
\end{figure}

@@

In the 200--400~km depth range, we observe a high wavespeed
anomaly within the Gulf of Mexico, which coincides spatially with the deepest
bathymetry and corresponds to a portion of ancient oceanic
Lithosphere~\citep{muller2008age}.
A remnant of the Juan de Fuca plate,
with a high wavespeed footprint, is visible at depths of 300~km and 400~km,
where SL2013NA shows a much stronger anomaly.
